Portable Multi- and Many-Core Performance for Finite Difference Codes; Application to the Free-Surface Component of NEMO.

### 2016-09-01 nemolite2d_perf.tex
nemolite-perf: update GPU-perf plots and captions so that we use psykal GPU numbers where appropriate

Our aim in this work is to achieve portable performance, especially
between multi-core CPU and many-core GPU systems. Consequently, we
have performed tests on both an Intel Ivy Bridge CPU (E5-2697 at
2.7~GHz) and on an NVIDIA Tesla K40 GPU.  On the Intel-based system we
have used the Gnu, Intel and Cray Fortran compilers (versions 4.9.1,
15.0.0.090 and 8.3.3, respectively). The code that made use of the GPU
was compiled using version 15.10 of the PGI compiler.

@@

\begin{figure}
\centering
\includegraphics[width=\picwidth]{gpu_opt_stages}
\caption{Performance of the various GPU implementations of NEMOLite2D.}
\label{FIG_gpu_opt_stages}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\picwidth]{cpu_cf_gpu}
\caption{Performance of the best OpenMP-parallel version of \psykal\
  NEMOLite2D (on a single Intel Ivy Bridge socket) compared with the best GPU implementation. {\bf This should really be best OpenACC version as that's what PSyclone can support.}}
\label{FIG_cpu_cf_gpu}
\end{figure}

@@

Having demonstrated that the \psykal\ separation of concerns may be
applied to finite-difference codes with minimal performance loss, our
next step will be to consider the automatic generation of the PSy
layer. In future work we will analyse the performance of a
domain-specific compiler that performs this task. This compiler
(which we have named `PSyclone') is currently under development.

>>>>

Our aim in this work is to achieve portable performance, especially
between multi-core CPU and many-core GPU systems. Consequently, we
have performed tests on both an Intel Ivy Bridge CPU (E5-2697 at
2.7~GHz) and on an NVIDIA Tesla K40 GPU.  On the Intel-based system we
have used the Gnu, Intel and Cray Fortran compilers (versions 4.9.1,
15.0.0.090 and 8.3.3, respectively). The code that made use of the GPU
was compiled using version 15.5 of the PGI compiler.

@@

\begin{figure}
\centering
\includegraphics[width=\picwidth]{gpu_opt_stages}
\caption{Performance of the \psykal\ (OpenACC) and CUDA GPU
  implementations of NEMOLite2D. The performance for the OpenACC
  version of the original code is not shown since it is identical to
  that of the \psykal\ version.}
\label{FIG_gpu_opt_stages}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\picwidth]{cpu_cf_gpu}
\caption{Performance of the best OpenMP-parallel version of \psykal\
  NEMOLite2D (on a single Intel Ivy Bridge socket) compared with the \psykal\ GPU implementation (using OpenACC).}
\label{FIG_cpu_cf_gpu}
\end{figure}

@@

Having demonstrated that the \psykal\ separation of concerns may be
applied to 2D finite-difference codes with minimal performance loss,
our next steps will be; 1) to consider the automatic generation of the
PSy layer and 2) to look at extending the approach to the full NEMO
model (i.e. three dimensions). In future work we will analyse the
performance of a domain-specific compiler that performs the automatic
generation of the PSy layer. This compiler (which we have named
`PSyclone') is currently under development.
